---
title: "Weight Stigma Dissertation Workflow (Positron + R)"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    code-summary: "Show code"
execute:
  echo: true
  warning: false
  message: false
---

# Overview

This tutorial runs a full dissertation workflow for nutrition-related social media text analysis, comparing:

- `weight_loss` posts
- `health_focused` posts

Research focus:

1. Is weight stigma present?
2. Is stigma more frequent in `weight_loss` content?
3. What words/phrases/themes are most common by category?
4. How do sentiment patterns differ?
5. How strongly do human coders agree?

::: {.callout-important}
## Conceptual Rule
Treat **weight stigma coding** and **sentiment analysis** as separate analyses.

- Human coding is the primary method for stigma identification.
- Lexicon sentiment is exploratory context, not a direct stigma measure.
:::

# Professional and Scope Statement

::: {.callout-important}
## Author, Credentials, and Contact
This tutorial was prepared by **Dr Chris Higton** (`f.higton@ucb.ac.uk`), a **Chartered Health Psychologist** and **HCPC-registered Practitioner Psychologist**.

Dr Higton is **not a dietitian**. This material is for research and education and should not be treated as individual dietetic or medical advice.

If you have questions about this tutorial, please email `f.higton@ucb.ac.uk`.
:::

# AI Authorship and Human-in-the-Loop

::: {.callout-important}
## Codex Support and Verification
This tutorial was developed with support from **Codex**.

All outputs were checked and validated by **Dr Chris Higton** before use.
:::

::: {.callout-warning}
## Human-in-the-Loop Rule
Do not use analysis, code, or written interpretation unless you understand the underlying logic and can explain it.

Analogy:
- It is often easier to **understand** spoken French than to **speak** French accurately.
- In the same way, generated code may look familiar, but you should only use what you can independently explain and defend.
:::

# Project Structure

Expected folders:

- `data_raw/`
- `data_clean/`
- `scripts/`
- `outputs/figures/`
- `outputs/tables/`
- `docs/codebook/`
- `report/`

::: {.callout-note}
## What is happening?
You are building a reproducible pipeline where each script does one job and writes outputs to fixed folders. This makes your methods auditable for dissertation marking and journal peer review.
:::

# Positron Setup (Quick Start)

## Download and Install

1. Install **R** from `https://cloud.r-project.org/` (Positron recommends R 4.2+ for R workflows).
2. Install **Positron** from `https://positron.posit.co/install.html`.
3. Open Positron and choose `File -> Open Folder...` to open your dissertation project folder.

::: {.callout-tip}
## Official Links
- Positron main page: `https://positron.posit.co/`
- Positron install guide: `https://positron.posit.co/install.html`
- R download: `https://cloud.r-project.org/`
:::

## Understanding Positron Panes

If you wrote "pains," this means **panes** in Positron.

- **Activity Bar**: switch between Explorer, Search, Source Control, Extensions.
- **Primary Side Bar**: file explorer and project navigation.
- **Editor**: where you write scripts and `.qmd` files.
- **Panel**: Console, Terminal, and Output.
- **Secondary Side Bar**: Session/Variables, Plots, Help, Viewer, Connections.

## Create the Dissertation Folder Structure in Positron Terminal

```{bash create_project_structure}
#| eval: false
mkdir -p dissertation-weight-stigma/{data_raw,data_clean,scripts,outputs/figures,outputs/tables,docs/codebook,report}
```

Then open that folder in Positron and place your scripts and data in the matching subfolders.

## Using Codex to Set Up Faster

You can ask Codex to scaffold the project and scripts, then you review outputs before running:

- "Create the folder structure and numbered scripts for my dissertation workflow."
- "Add defensive checks and save outputs to `outputs/tables` and `outputs/figures`."
- "Generate a codebook template and coder instructions."

::: {.callout-warning}
## Check Before Running
Always verify generated code, package versions, API terms, and ethics constraints before large data collection runs.
:::

::: {.callout-warning}
## Digital Divide, Equity, and AI Policy
If AI tools are expected for coursework or research productivity, access should be equitable.

- Be careful about the digital divide (device quality, connectivity, paid tool access, accessibility needs).
- UCB should provide or signpost equitable access to approved LLM tools where needed.
- UCB AI policy is being updated, so always check the latest institutional guidance before submission.
:::

# Recommended Reading and Core References

Use these resources to strengthen methods, transparency, and reproducibility:

- **Methods in Ecology and Evolution article** (link provided): `https://besjournals.onlinelibrary.wiley.com/doi/10.1111/2041-210x.70267`
- **Text Mining with R (tidy text methods)**: `https://www.tidytextmining.com/`
- **R for Data Science (2e)**: `https://r4ds.hadley.nz/`

::: {.callout-note}
## How to use these in your dissertation
- Use *Text Mining with R* to justify tokenisation, sentiment lexicon workflows, and n-gram logic.
- Use *R for Data Science* for reproducible workflow standards (projects, wrangling, plotting, and communication).
- Use the linked *Methods in Ecology and Evolution* paper as a methods-critical reference where relevant to your study design and reporting.
:::

# Script Run Order

Run the in-document sections in this order:

1. `1) Setup`
2. `2) Import + Clean + Tokenise`
3. `3) Frequency + N-grams + TF-IDF`
4. `4) Sentiment Analysis (Exploratory)`
5. `5) Build Codebook + Coder Template`
6. `6) Inter-rater Reliability`
7. `7) Statistical Comparison of Stigma by Category`

::: {.callout-tip}
## Code Dropdowns
Each section uses Quarto code dropdown options (`code-fold`) so you can expand/collapse code as needed.
Click **Show code** to open the code box for that section.
:::

::: {.callout-tip}
## Raw Data Location
Put your social media CSV files in `data_raw/` before running section `2) Import + Clean + Tokenise`.

Required columns:
`post_id`, `platform`, `date`, `author`, `text`, `url`, `category`
:::

# Responsible Scraping (If You Collect Data Yourself)

::: {.callout-warning}
## Avoid Overloading Websites
When scraping posts, collect data slowly and respectfully.

- Check `robots.txt` and platform Terms of Service first.
- Prefer official APIs when available.
- Add delays between requests (for example 2-5 seconds plus random jitter).
- Use pagination limits and cap requests per minute.
- Use a clear `User-Agent` that identifies a research contact.
- Stop or slow down when you receive `429` or `503` responses.
- Retry with exponential backoff instead of rapid repeated requests.
- Cache results locally so you do not repeatedly hit the same URLs.
:::

```{r polite_scraping_example}
#| eval: false
# Example polite request pattern (httr2)
library(httr2)

safe_get <- function(url, pause_seconds = 3, max_tries = 5) {
  for (i in seq_len(max_tries)) {
    Sys.sleep(pause_seconds + runif(1, 0, 1.5))

    resp <- request(url) |>
      req_user_agent("MSc-dietetics-research/0.1 (contact: f.higton@ucb.ac.uk)") |>
      req_perform()

    status <- resp_status(resp)

    if (status < 400) return(resp)

    if (status %in% c(429, 503)) {
      # Exponential backoff reduces pressure on the host server.
      Sys.sleep(2 ^ i)
    } else {
      break
    }
  }
  stop("Request failed after retries: ", url)
}
```

::: {.callout-note}
## Detailed Explanation of This Example
1. `safe_get()` is a wrapper function for web requests that prioritizes server safety and research ethics.
2. `pause_seconds + runif(1, 0, 1.5)` adds a base pause and random jitter, so your requests do not look like a bot hammering a site at fixed intervals.
3. `req_user_agent(...)` clearly identifies your project and provides a contact email, which is good professional practice.
4. `resp_status(resp)` checks the HTTP status code after each request.
5. If status is below 400, the request succeeded and the response is returned immediately.
6. If status is `429` (rate limit) or `503` (service unavailable), the code waits longer each time with `2 ^ i` (exponential backoff) before retrying.
7. `max_tries` prevents infinite retry loops and limits server pressure.
8. The final `stop(...)` ensures failed URLs are logged as explicit errors so you can report exclusions transparently.
9. To adapt this for your dissertation, keep `pause_seconds` conservative and record your retry policy in Methods.
:::

::: {.callout-note}
## What is happening?
These safeguards reduce risk of overloading websites and improve ethical transparency.
In your methods section, report your request rate, delay policy, and how you handled rate limits.
:::

# Package Options by Scraping Type

::: {.callout-note}
## Package List You Can Use
As of **April 21, 2026**, these are common R options for different scraping/data-ingestion tasks.
:::

## 1) General Web Scraping

- `rvest`: most common for HTML scraping.
- `httr`: HTTP requests (`GET`, `POST`) and API interaction.
- `RCurl`: lower-level `libcurl` interface.
- `xml2`: parse/process HTML and XML.

## 2) Structured Data (Tables, JSON, APIs)

- `jsonlite`: parse/convert JSON.
- `tidyjson`: work with deeply nested JSON in tidy workflows.
- `httr` (or `httr2`): API requests and authentication flows.

## 3) Dynamic / JavaScript-Rendered Pages

- `RSelenium`: browser automation for JS-rendered content.
- `webdriver`: browser control package (historically tied to PhantomJS workflows).
- `rvest + splashr`: older headless-browser pattern for JS-heavy pages.

::: {.callout-warning}
## Practical Note
For many modern JS pages, `chromote` is often a more current option than older PhantomJS-based workflows.
:::

## 4) Scraping and Parsing PDFs

- `pdftools`: extract text/metadata/render pages.
- `tm`: text mining pipeline on extracted text.
- `tabulizer`: extract tables from PDFs.

## 5) Social Media Data Collection

- `rtweet`: X/Twitter API workflows (package status changes; verify current availability).
- `Rfacebook`: Facebook API package (legacy; API access is heavily restricted).
- `twitteR`: older Twitter package (legacy).
- `RedditExtractoR`: toolkit for structured Reddit thread extraction.
- `rtoot`: Mastodon API package for federated instance data collection.

::: {.callout-warning}
## Status Snapshot (as of April 21, 2026)
- `rtweet` was archived/removed from CRAN on **April 7, 2025**.
- `twitteR` was archived/removed from CRAN on **February 17, 2025**.
- `Rfacebook` remains an older package (last CRAN release in 2017), so compatibility with current Facebook/Meta API policy can be limited.
:::

::: {.callout-important}
## API Reality Check
For social media platforms, API terms, pricing tiers, and accessible endpoints change frequently. Always confirm current policy before data collection and include this in methods/ethics reporting.
:::

## Reddit-Specific Notes

- Prefer Reddit's official API routes and follow current developer terms.
- Use conservative request rates and documented pagination.
- Keep a transparent sampling log (subreddits, search terms, date window, pull date).

```{r reddit_collection_example}
#| eval: false
install.packages("RedditExtractoR")
library(RedditExtractoR)

# Example: find relevant threads, then pull thread + comment content
thread_urls <- find_thread_urls(
  keywords = "weight stigma nutrition",
  subreddit = "nutrition",
  sort_by = "top",
  period = "year"
)

reddit_data <- get_thread_content(thread_urls$url[1:50])
```

::: {.callout-note}
## Detailed Explanation of This Example
1. `find_thread_urls(...)` first builds a sampling frame of relevant thread URLs, rather than scraping random pages.
2. `keywords` defines your topic filter (`"weight stigma nutrition"`).
3. `subreddit = "nutrition"` narrows scope to one community, which improves methodological clarity.
4. `sort_by = "top"` and `period = "year"` define how posts are ranked and over what window.
5. `get_thread_content(...)` then retrieves structured thread metadata and comment content from selected URLs.
6. `thread_urls$url[1:50]` caps collection to a manageable subset for pilot analysis; increase only after checking feasibility and ethics.
7. In reporting, state exactly how many threads were initially found and how many were retained.
8. Save raw pulls and cleaned pulls separately so you can audit preprocessing decisions.
:::

## Mastodon-Specific Notes

- Mastodon is federated, so instance choice matters (`mastodon.social`, `fosstodon.org`, etc.).
- Record the instance and whether data are local/global timeline pulls.
- Use `rtoot` token/auth workflows where required.

```{r mastodon_collection_example}
#| eval: false
install.packages("rtoot")
library(rtoot)

# Public timeline example (anonymous where allowed):
mastodon_posts <- get_timeline_public(
  instance = "mastodon.social",
  limit = 100,
  anonymous = TRUE
)
```

::: {.callout-note}
## Detailed Explanation of This Example
1. `rtoot` connects to Mastodon APIs in a tidy R workflow.
2. `get_timeline_public(...)` queries public posts from a selected instance.
3. `instance = "mastodon.social"` is critical because Mastodon is federated; different instances can produce different discourse samples.
4. `limit = 100` sets a clear sample cap for one request pass.
5. `anonymous = TRUE` attempts an unauthenticated request where allowed by the target instance.
6. If you need deeper or repeated pulls, use authenticated tokens and document token scope and collection dates.
7. For reproducibility, record whether you used local timeline filtering and any pagination strategy.
:::

## Bluesky-Specific Options

- `bskyr`: R package for Bluesky/AT Protocol workflows.
- `httr` + `jsonlite`: useful fallback for custom endpoint calls.

```{r bluesky_collection_example}
#| eval: false
# Recommended first option for Bluesky:
install.packages("bskyr")
library(bskyr)

# If you need a custom endpoint, use httr/jsonlite:
library(httr)
library(jsonlite)
```

::: {.callout-note}
## Detailed Explanation of This Example
1. `bskyr` is the high-level option for most Bluesky data tasks in R.
2. Installing and loading `bskyr` gives you endpoint-specific helper functions with tidy outputs.
3. `httr` + `jsonlite` is shown as a fallback for endpoints not yet wrapped by `bskyr`.
4. This two-path approach is practical for dissertation work: start with stable wrappers, then use low-level API calls only when needed.
5. If you use low-level calls, document endpoint URLs, parameters, and response schema decisions in Methods.
:::

# Platform Status Caveats (Important)

::: {.callout-warning}
## Keep This Updated in Your Dissertation
- Some packages above are legacy or may be archived.
- Availability on CRAN can change over time.
- Platform APIs can become read-limited or paid-only.

In your final methods chapter, include the exact package versions and access conditions used at the time of collection.
:::

# Visualise Data for Dissertation Outputs

Use visuals to complement coding results, not replace them.

- Frequency bar charts: show dominant vocabulary by category.
- TF-IDF comparisons: show distinctive terms.
- Sentiment plots: show exploratory polarity/emotion distributions.
- Stacked stigma plots: show prevalence and subtype composition.
- Reliability visuals: confusion matrix and disagreement summaries.

```{r visualisation_example_plot}
#| eval: false
library(readr)
library(ggplot2)

stigma_prev <- read_csv("outputs/tables/stigma_prevalence_by_category.csv")

ggplot(stigma_prev, aes(category, percent, fill = stigma_binary)) +
  geom_col() +
  labs(
    title = "Weight Stigma Prevalence by Category",
    x = NULL,
    y = "Percent of posts",
    fill = "Stigma"
  ) +
  theme_minimal(base_size = 12)
```

::: {.callout-note}
## Detailed Explanation of This Example
1. The table `stigma_prevalence_by_category.csv` is read from your saved outputs, ensuring your figure is generated from reproducible analysis files.
2. `aes(category, percent, fill = stigma_binary)` maps category to x-axis, prevalence to y-axis, and stigma presence/absence to bar color.
3. `geom_col()` draws bars directly from the provided percentages.
4. `labs(...)` applies publication-ready labels for dissertation figures.
5. `theme_minimal(base_size = 12)` improves readability and keeps style clean for academic reporting.
6. To improve journal readiness, set a fixed color palette across all figures and export with high DPI.
:::

::: {.callout-note}
## What is happening?
This ensures your dissertation includes clear, publication-ready figures linked directly to saved analysis tables.
:::

# 1) Setup

```{r section_01_setup}
#| eval: false
#| code-fold: true
#| code-summary: "Show setup code (packages + helper functions)"
# 01 setup (self-contained in this QMD)

required_packages <- c(
  "tidyverse",
  "tidytext",
  "textdata",
  "janitor",
  "lubridate",
  "stringi",
  "SnowballC",
  "here",
  "irr",
  "effectsize",
  "scales",
  "patchwork"
)

missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, FUN.VALUE = logical(1), quietly = TRUE)
]

if (length(missing_packages) > 0) {
  install.packages(missing_packages, repos = "https://cloud.r-project.org")
}

invisible(lapply(required_packages, library, character.only = TRUE))

# Shared helper utilities used in later sections
project_paths <- list(
  raw = here::here("data_raw"),
  clean = here::here("data_clean"),
  outputs = here::here("outputs"),
  figures = here::here("outputs", "figures"),
  tables = here::here("outputs", "tables"),
  codebook = here::here("docs", "codebook"),
  ratings = here::here("docs", "codebook", "ratings"),
  report = here::here("report")
)

invisible(lapply(project_paths, dir.create, recursive = TRUE, showWarnings = FALSE))

required_columns <- c(
  "post_id", "platform", "date", "author", "text", "url", "category"
)

check_required_columns <- function(df, required = required_columns) {
  missing_cols <- setdiff(required, names(df))
  if (length(missing_cols) > 0) {
    stop(
      "Missing required columns: ",
      paste(missing_cols, collapse = ", "),
      call. = FALSE
    )
  }
}

normalise_category <- function(x) {
  x <- stringr::str_to_lower(x)
  x <- stringr::str_replace_all(x, "[-\\s]+", "_")
  x
}

save_table <- function(df, file_name) {
  readr::write_csv(df, here::here("outputs", "tables", file_name), na = "")
}

save_plot <- function(plot_obj, file_name, width = 10, height = 6, dpi = 320) {
  ggplot2::ggsave(
    filename = here::here("outputs", "figures", file_name),
    plot = plot_obj,
    width = width,
    height = height,
    dpi = dpi,
    bg = "white"
  )
}

interpret_kappa <- function(kappa_value) {
  dplyr::case_when(
    is.na(kappa_value) ~ "Not available",
    kappa_value < 0.00 ~ "Less than chance agreement",
    kappa_value < 0.21 ~ "Slight agreement",
    kappa_value < 0.41 ~ "Fair agreement",
    kappa_value < 0.61 ~ "Moderate agreement",
    kappa_value < 0.81 ~ "Substantial agreement",
    TRUE ~ "Almost perfect agreement"
  )
}

message("Setup complete.")
message("Place raw CSV files in: ", here::here("data_raw"))
message("Outputs will be saved to: ", here::here("outputs"))
```

::: {.callout-note}
## What is happening?
This installs missing packages, loads the required libraries, and confirms your output folders exist.
:::

# 2) Import + Clean + Tokenise

```{r section_02_import_clean_tokenise}
#| eval: false
#| code-fold: true
#| code-summary: "Show import, cleaning, and tokenisation code"
# 02 import + clean + tokenise
# Assumes setup chunk has already been run in this QMD session.

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidytext)
  library(janitor)
  library(lubridate)
  library(stringi)
  library(SnowballC)
  library(here)
})

raw_files <- list.files(project_paths$raw, pattern = "\\.csv$", full.names = TRUE)

if (length(raw_files) == 0) {
  stop("No CSV files found in data_raw/. Add at least one CSV and rerun.", call. = FALSE)
}

raw_posts <- purrr::map_dfr(
  raw_files,
  ~ readr::read_csv(.x, show_col_types = FALSE) %>%
    mutate(source_file = basename(.x))
)

raw_posts <- janitor::clean_names(raw_posts)
check_required_columns(raw_posts)

allowed_categories <- c("weight_loss", "health_focused")
do_stemming <- FALSE

clean_posts <- raw_posts %>%
  mutate(
    category = normalise_category(category),
    category = if_else(category %in% allowed_categories, category, NA_character_),
    date_parsed = suppressWarnings(
      parse_date_time(
        as.character(date),
        orders = c(
          "Ymd HMS", "Ymd HM", "Ymd", "dmy HMS", "dmy HM", "dmy",
          "mdy HMS", "mdy HM", "mdy", "Y-m-d", "Y/m/d"
        ),
        tz = "UTC"
      )
    ),
    text_original = text,
    text_no_url = str_remove_all(text_original, "https?://\\S+|www\\.\\S+"),
    text_no_emoji = stringi::stri_replace_all_regex(text_no_url, "[\\p{So}\\p{Cn}]", " "),
    text_no_punct = str_replace_all(text_no_emoji, "[[:punct:]]+", " "),
    text_no_num = str_replace_all(text_no_punct, "[[:digit:]]+", " "),
    text_clean = text_no_num %>% str_to_lower() %>% str_squish()
  ) %>%
  filter(!is.na(text_clean), text_clean != "")

if (any(is.na(clean_posts$category))) {
  warning("Some rows have categories outside {weight_loss, health_focused}. They are kept with NA category.")
}

readr::write_csv(clean_posts, here::here("data_clean", "posts_clean.csv"), na = "")
saveRDS(clean_posts, here::here("data_clean", "posts_clean.rds"))

tokens <- clean_posts %>%
  select(post_id, category, date_parsed, text_clean) %>%
  unnest_tokens(word, text_clean) %>%
  filter(str_detect(word, "^[a-z']+$")) %>%
  anti_join(stop_words, by = "word")

if (do_stemming) {
  tokens <- tokens %>% mutate(word = SnowballC::wordStem(word))
}

readr::write_csv(tokens, here::here("data_clean", "tokens_no_stop.csv"), na = "")

message("Saved cleaned posts to data_clean/posts_clean.csv")
message("Saved token dataset to data_clean/tokens_no_stop.csv")
```

::: {.callout-note}
## What is happening?
This code merges all CSV files, standardises categories, cleans text (URLs/punctuation/numbers/emojis), lowercases text, removes stopwords, and creates token-level data for analysis.
:::

Saved files:

- `data_clean/posts_clean.csv`
- `data_clean/posts_clean.rds`
- `data_clean/tokens_no_stop.csv`

# 3) Frequency + N-grams + TF-IDF

```{r section_03_frequency_ngrams_tfidf}
#| eval: false
#| code-fold: true
#| code-summary: "Show frequency, n-gram, and TF-IDF code"
# 03 frequency + n-grams + TF-IDF

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidytext)
  library(scales)
  library(here)
})

tokens <- readr::read_csv(here::here("data_clean", "tokens_no_stop.csv"), show_col_types = FALSE)
clean_posts <- readr::read_csv(here::here("data_clean", "posts_clean.csv"), show_col_types = FALSE)

if (nrow(tokens) == 0) {
  stop("Token dataset is empty. Run the import/clean/tokenise section first.", call. = FALSE)
}

overall_words <- tokens %>% count(word, sort = TRUE)
words_by_category <- tokens %>% count(category, word, sort = TRUE)

stop_words_vec <- tidytext::stop_words$word

bigrams <- clean_posts %>%
  select(post_id, category, text_clean) %>%
  unnest_tokens(bigram, text_clean, token = "ngrams", n = 2) %>%
  separate(bigram, into = c("word1", "word2"), sep = " ", fill = "right", extra = "drop") %>%
  filter(
    !is.na(word1), !is.na(word2),
    !word1 %in% stop_words_vec,
    !word2 %in% stop_words_vec
  ) %>%
  unite(bigram, word1, word2, sep = " ") %>%
  count(category, bigram, sort = TRUE)

trigrams <- clean_posts %>%
  select(post_id, category, text_clean) %>%
  unnest_tokens(trigram, text_clean, token = "ngrams", n = 3) %>%
  separate(trigram, into = c("word1", "word2", "word3"), sep = " ", fill = "right", extra = "drop") %>%
  filter(
    !is.na(word1), !is.na(word2), !is.na(word3),
    !word1 %in% stop_words_vec,
    !word2 %in% stop_words_vec,
    !word3 %in% stop_words_vec
  ) %>%
  unite(trigram, word1, word2, word3, sep = " ") %>%
  count(category, trigram, sort = TRUE)

tfidf_terms <- tokens %>%
  count(category, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = category, n = n) %>%
  arrange(desc(tf_idf))

save_table(overall_words, "top_words_overall.csv")
save_table(words_by_category, "top_words_by_category.csv")
save_table(bigrams, "top_bigrams_by_category.csv")
save_table(trigrams, "top_trigrams_by_category.csv")
save_table(tfidf_terms, "tfidf_by_category.csv")

plot_overall <- overall_words %>%
  slice_max(order_by = n, n = 20, with_ties = FALSE) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = n, y = word)) +
  geom_col(fill = "#0D5C63") +
  scale_x_continuous(labels = comma) +
  labs(
    title = "Top 20 Words Overall",
    x = "Frequency",
    y = NULL
  ) +
  theme_minimal(base_size = 12)

plot_by_category <- words_by_category %>%
  filter(!is.na(category)) %>%
  group_by(category) %>%
  slice_max(order_by = n, n = 15, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(word = tidytext::reorder_within(word, n, category)) %>%
  ggplot(aes(x = n, y = word, fill = category)) +
  geom_col(show.legend = FALSE) +
  tidytext::scale_y_reordered() +
  facet_wrap(~ category, scales = "free_y") +
  scale_x_continuous(labels = comma) +
  labs(
    title = "Top Words by Category",
    x = "Frequency",
    y = NULL
  ) +
  theme_minimal(base_size = 12)

plot_tfidf <- tfidf_terms %>%
  filter(!is.na(category)) %>%
  group_by(category) %>%
  slice_max(order_by = tf_idf, n = 15, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(word = tidytext::reorder_within(word, tf_idf, category)) %>%
  ggplot(aes(x = tf_idf, y = word, fill = category)) +
  geom_col(show.legend = FALSE) +
  tidytext::scale_y_reordered() +
  facet_wrap(~ category, scales = "free_y") +
  labs(
    title = "Most Distinctive Terms by Category (TF-IDF)",
    x = "TF-IDF",
    y = NULL
  ) +
  theme_minimal(base_size = 12)

save_plot(plot_overall, "word_frequency_overall.png")
save_plot(plot_by_category, "word_frequency_by_category.png")
save_plot(plot_tfidf, "tfidf_by_category.png")

message("Frequency, n-gram, and TF-IDF outputs saved.")
```

::: {.callout-note}
## What is happening?
This quantifies language patterns:

- high-frequency terms
- common bigrams/trigrams
- terms that are distinctive in each category (TF-IDF)

These outputs describe language differences but do not prove stigma on their own.
:::

Saved outputs:

- Tables in `outputs/tables/`
- Figures in `outputs/figures/`

# 4) Sentiment Analysis (Exploratory)

```{r section_04_sentiment_analysis}
#| eval: false
#| code-fold: true
#| code-summary: "Show sentiment analysis code"
# 04 sentiment analysis (exploratory, complementary only)

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidytext)
  library(scales)
  library(here)
})

tokens <- readr::read_csv(here::here("data_clean", "tokens_no_stop.csv"), show_col_types = FALSE)

if (nrow(tokens) == 0) {
  stop("Token dataset is empty. Run the import/clean/tokenise section first.", call. = FALSE)
}

# BING
bing_sent <- tokens %>%
  inner_join(get_sentiments("bing"), by = "word")

overall_bing <- bing_sent %>%
  count(sentiment, sort = TRUE) %>%
  mutate(prop = n / sum(n))

by_category_bing <- bing_sent %>%
  filter(!is.na(category)) %>%
  count(category, sentiment, sort = TRUE) %>%
  group_by(category) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup()

# NRC (optional if lexicon unavailable in non-interactive sessions)
nrc_lexicon <- tryCatch(
  get_sentiments("nrc"),
  error = function(e) {
    warning("NRC lexicon unavailable. Skipping NRC emotion outputs. Details: ", e$message)
    NULL
  }
)

if (!is.null(nrc_lexicon)) {
  nrc_sent <- tokens %>%
    inner_join(nrc_lexicon, by = "word")

  nrc_emotions <- nrc_sent %>%
    filter(!sentiment %in% c("positive", "negative"), !is.na(category)) %>%
    count(category, sentiment, sort = TRUE)
} else {
  nrc_emotions <- tibble(
    category = character(),
    sentiment = character(),
    n = integer()
  )
}

# AFINN (optional if lexicon unavailable in non-interactive sessions)
afinn_lexicon <- tryCatch(
  get_sentiments("afinn"),
  error = function(e) {
    warning("AFINN lexicon unavailable. Skipping AFINN outputs. Details: ", e$message)
    NULL
  }
)

if (!is.null(afinn_lexicon)) {
  afinn_scores <- tokens %>%
    inner_join(afinn_lexicon, by = "word") %>%
    group_by(post_id, category) %>%
    summarise(
      afinn_mean = mean(value, na.rm = TRUE),
      afinn_sum = sum(value, na.rm = TRUE),
      matched_tokens = dplyr::n(),
      .groups = "drop"
    )

  afinn_summary <- afinn_scores %>%
    filter(!is.na(category)) %>%
    group_by(category) %>%
    summarise(
      mean_afinn = mean(afinn_mean, na.rm = TRUE),
      median_afinn = median(afinn_mean, na.rm = TRUE),
      sd_afinn = sd(afinn_mean, na.rm = TRUE),
      posts_with_scores = dplyr::n(),
      .groups = "drop"
    )
} else {
  afinn_scores <- tibble(
    post_id = character(),
    category = character(),
    afinn_mean = numeric(),
    afinn_sum = numeric(),
    matched_tokens = integer()
  )
  afinn_summary <- tibble(
    category = character(),
    mean_afinn = numeric(),
    median_afinn = numeric(),
    sd_afinn = numeric(),
    posts_with_scores = integer()
  )
}

save_table(overall_bing, "sentiment_overall_bing.csv")
save_table(by_category_bing, "sentiment_by_category_bing.csv")
save_table(nrc_emotions, "sentiment_nrc_emotions_by_category.csv")
save_table(afinn_scores, "sentiment_afinn_post_scores.csv")
save_table(afinn_summary, "sentiment_afinn_summary_by_category.csv")

plot_bing <- by_category_bing %>%
  ggplot(aes(x = category, y = prop, fill = sentiment)) +
  geom_col(position = "stack") +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_manual(values = c(negative = "#B23A48", positive = "#2A9D8F")) +
  labs(
    title = "Sentiment Composition by Category (BING)",
    x = NULL,
    y = "Proportion of matched sentiment words",
    fill = "Sentiment"
  ) +
  theme_minimal(base_size = 12)

if (nrow(nrc_emotions) > 0) {
  plot_nrc <- nrc_emotions %>%
    group_by(category) %>%
    slice_max(order_by = n, n = 8, with_ties = FALSE) %>%
    ungroup() %>%
    mutate(sentiment = tidytext::reorder_within(sentiment, n, category)) %>%
    ggplot(aes(x = n, y = sentiment, fill = category)) +
    geom_col(show.legend = FALSE) +
    tidytext::scale_y_reordered() +
    facet_wrap(~ category, scales = "free_y") +
    scale_x_continuous(labels = comma) +
    labs(
      title = "Top NRC Emotion Terms by Category",
      x = "Count",
      y = NULL
    ) +
    theme_minimal(base_size = 12)
}

if (nrow(afinn_scores) > 0) {
  plot_afinn <- afinn_scores %>%
    filter(!is.na(category)) %>%
    ggplot(aes(x = category, y = afinn_mean, fill = category)) +
    geom_boxplot(alpha = 0.8, width = 0.55, show.legend = FALSE) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey30") +
    labs(
      title = "Distribution of AFINN Scores by Category",
      x = NULL,
      y = "Mean AFINN score per post"
    ) +
    theme_minimal(base_size = 12)
}

save_plot(plot_bing, "sentiment_bing_by_category.png")
if (nrow(nrc_emotions) > 0) {
  save_plot(plot_nrc, "sentiment_nrc_by_category.png")
}
if (nrow(afinn_scores) > 0) {
  save_plot(plot_afinn, "sentiment_afinn_by_category.png")
}

message("Sentiment tables and figures saved.")
```

::: {.callout-warning}
## What is happening?
This uses lexicons (`bing`, `nrc`, `afinn`) to summarise emotional polarity and valence patterns.

Interpretation caution for dietetics research:
- nutrition language can be context-dependent;
- lexicons can miss irony, clinical nuance, and stigma expressed without emotional words.
:::

# 5) Build Codebook + Coder Template

```{r section_05_codebook_coder_template}
#| eval: false
#| code-fold: true
#| code-summary: "Show codebook and coder template code"
# 05 codebook + coder template

suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
})

codebook <- tibble::tribble(
  ~code, ~label, ~definition, ~include_if, ~exclude_if, ~example,
  "stigma_binary", "Weight stigma present (1) vs absent (0)",
  "Overall decision for whether the post contains weight-stigmatising content.",
  "Any explicit or implied demeaning, blaming, shaming, stereotyping, or moral judgement about body weight.",
  "Neutral, supportive, or clinical discussion without demeaning language.",
  "'People are overweight because they are lazy.'",

  "explicit_blame", "Explicit blame",
  "Directly attributes higher body weight to personal moral failure or laziness.",
  "Statements that assign fault to individuals for body size.",
  "Structural/contextual discussion without blame.",
  "'No excuses, weight gain is your own fault.'",

  "moralising_food_body", "Moralising food/body language",
  "Frames foods or bodies as morally good/bad, clean/dirty, worthy/unworthy.",
  "Good/bad person framing based on eating or body size.",
  "Practical nutrition advice without moral labels.",
  "'Cheat meals make you weak and disgusting.'",

  "appearance_judgement", "Appearance-focused judgement",
  "Judges personal worth or social value based on body appearance.",
  "Ridicule, disgust, or social devaluation tied to body shape.",
  "Neutral reference to appearance in a non-judgemental context.",
  "'Beach bodies are for disciplined people only.'",

  "stereotyping_larger_bodies", "Stereotyping larger bodies",
  "Uses generalisations about people in larger bodies as a group.",
  "Claims that a group is lazy, undisciplined, unhealthy, etc.",
  "Post-specific behaviour without broad group assumptions.",
  "'Overweight people never care about health.'",

  "healthism_personal_failure", "Healthism / implied personal failure",
  "Implies health status is fully controlled by individual choices and willpower.",
  "Ignores social, medical, economic, or environmental determinants of health.",
  "Balanced discussion of multiple determinants.",
  "'If you are sick, you just didn't try hard enough.'",

  "neutral_supportive", "Neutral/supportive/non-stigmatising",
  "Content that is supportive, neutral, or non-judgemental.",
  "Person-centred, empathetic, non-shaming tone.",
  "Any explicit stigmatizing language.",
  "'Health goals should be tailored and respectful to each person.'"
)

readr::write_csv(codebook, here::here("docs", "codebook", "weight_stigma_codebook.csv"), na = "")

coder_instructions <- c(
  "# Coder Instructions: Weight Stigma in Nutrition-Related Posts",
  "",
  "## Aim",
  "Classify each post for weight stigma using the codebook in this folder.",
  "",
  "## Core principles",
  "1. Code stigma separately from sentiment. A negative tone is not automatically stigma.",
  "2. Use the full post context before assigning codes.",
  "3. Assign stigma_binary = 1 when any stigma category applies.",
  "4. Assign stigma_binary = 0 when no stigma categories apply.",
  "5. Mark neutral_supportive = 1 when language is clearly non-stigmatising.",
  "",
  "## Coding steps",
  "1. Read post text once for context.",
  "2. Decide stigma_binary (1/0).",
  "3. Apply all relevant multi-codes (1 = present, 0 = absent).",
  "4. Add short justification in notes for difficult cases.",
  "",
  "## Independent coding",
  "Each coder should complete their own file without discussing coding decisions until reliability is calculated.",
  "",
  "## File naming",
  "Save your file as docs/codebook/ratings/coder_<initials>.csv"
)

writeLines(coder_instructions, here::here("docs", "codebook", "coder_instructions.md"))

posts_path <- here::here("data_clean", "posts_clean.csv")

if (file.exists(posts_path)) {
  posts <- readr::read_csv(posts_path, show_col_types = FALSE)
} else {
  posts <- readr::read_csv(here::here("data_clean", "example_cleaned_posts.csv"), show_col_types = FALSE)
}

coder_template <- posts %>%
  transmute(
    post_id,
    platform,
    date = date,
    category,
    text,
    url,
    stigma_binary = NA_integer_,
    explicit_blame = NA_integer_,
    moralising_food_body = NA_integer_,
    appearance_judgement = NA_integer_,
    stereotyping_larger_bodies = NA_integer_,
    healthism_personal_failure = NA_integer_,
    neutral_supportive = NA_integer_,
    notes = NA_character_,
    coder_id = NA_character_
  )

readr::write_csv(coder_template, here::here("docs", "codebook", "coder_template.csv"), na = "")

message("Codebook saved to docs/codebook/weight_stigma_codebook.csv")
message("Coder template saved to docs/codebook/coder_template.csv")
```

::: {.callout-note}
## What is happening?
This generates a draft stigma codebook and a coder template with binary + multi-code columns.

Coders should rate independently and save files to `docs/codebook/ratings/`.
:::

Generated files:

- `docs/codebook/weight_stigma_codebook.csv`
- `docs/codebook/coder_instructions.md`
- `docs/codebook/coder_template.csv`

# 6) Inter-rater Reliability

```{r section_06_interrater_reliability}
#| eval: false
#| code-fold: true
#| code-summary: "Show inter-rater reliability code"
# 06 inter-rater reliability

suppressPackageStartupMessages({
  library(tidyverse)
  library(janitor)
  library(irr)
  library(here)
})

rating_files <- list.files(project_paths$ratings, pattern = "\\.csv$", full.names = TRUE)

if (length(rating_files) == 0) {
  stop(
    "No coder rating files found in docs/codebook/ratings/. Add coder CSV files and rerun.",
    call. = FALSE
  )
}

ratings_long <- purrr::map_dfr(
  rating_files,
  ~ readr::read_csv(.x, show_col_types = FALSE) %>%
    janitor::clean_names() %>%
    mutate(source_file = basename(.x))
)

required_rating_cols <- c("post_id", "stigma_binary")
missing_rating_cols <- setdiff(required_rating_cols, names(ratings_long))
if (length(missing_rating_cols) > 0) {
  stop(
    "Rating files must include columns: post_id, stigma_binary. Missing: ",
    paste(missing_rating_cols, collapse = ", "),
    call. = FALSE
  )
}

if (!"coder_id" %in% names(ratings_long)) {
  ratings_long <- ratings_long %>%
    mutate(coder_id = stringr::str_remove(source_file, "\\.csv$"))
}

ratings_long <- ratings_long %>%
  mutate(stigma_binary = as.character(stigma_binary)) %>%
  filter(!is.na(post_id), !is.na(coder_id), !is.na(stigma_binary)) %>%
  distinct(post_id, coder_id, .keep_all = TRUE)

ratings_wide <- ratings_long %>%
  select(post_id, coder_id, stigma_binary) %>%
  pivot_wider(names_from = coder_id, values_from = stigma_binary)

coder_cols <- setdiff(names(ratings_wide), "post_id")

if (length(coder_cols) < 2) {
  stop("At least two coders are required for reliability analysis.", call. = FALSE)
}

results <- list()

cohen_data <- ratings_wide %>%
  select(all_of(coder_cols[1:2])) %>%
  drop_na() %>%
  mutate(across(everything(), as.factor))

if (nrow(cohen_data) > 0) {
  cohen <- irr::kappa2(cohen_data, weight = "unweighted")
  cohen_kappa <- unname(cohen$value)
  results$cohen <- tibble(
    metric = "Cohen's kappa",
    raters = paste(coder_cols[1], coder_cols[2], sep = " vs "),
    value = cohen_kappa,
    interpretation = interpret_kappa(cohen_kappa)
  )

  confusion <- table(
    rater_1 = cohen_data[[1]],
    rater_2 = cohen_data[[2]]
  )

  confusion_df <- as.data.frame(confusion) %>%
    rename(count = Freq)

  save_table(confusion_df, "reliability_confusion_matrix.csv")

  confusion_plot <- confusion_df %>%
    ggplot(aes(x = rater_1, y = rater_2, fill = count)) +
    geom_tile() +
    geom_text(aes(label = count), color = "white", fontface = "bold") +
    scale_fill_gradient(low = "#4A6FA5", high = "#1B1B3A") +
    labs(
      title = "Confusion Matrix: First Two Coders",
      x = coder_cols[1],
      y = coder_cols[2],
      fill = "Count"
    ) +
    theme_minimal(base_size = 12)

  save_plot(confusion_plot, "reliability_confusion_matrix.png", width = 7, height = 6)
} else {
  warning("No overlapping non-missing rows for the first two coders. Cohen's kappa not computed.")
}

if (length(coder_cols) > 2) {
  fleiss_data <- ratings_wide %>%
    select(all_of(coder_cols)) %>%
    drop_na() %>%
    mutate(across(everything(), as.factor))

  if (nrow(fleiss_data) > 0) {
    fleiss <- irr::kappam.fleiss(as.matrix(fleiss_data))
    fleiss_kappa <- unname(fleiss$value)
    results$fleiss <- tibble(
      metric = "Fleiss' kappa",
      raters = paste(length(coder_cols), "coders"),
      value = fleiss_kappa,
      interpretation = interpret_kappa(fleiss_kappa)
    )
  } else {
    warning("No complete rows across all coders. Fleiss' kappa not computed.")
  }
}

disagreements <- ratings_wide %>%
  rowwise() %>%
  mutate(disagree = dplyr::n_distinct(stats::na.omit(c_across(all_of(coder_cols)))) > 1) %>%
  ungroup() %>%
  filter(disagree)

posts_path <- here::here("data_clean", "posts_clean.csv")
if (file.exists(posts_path)) {
  posts <- readr::read_csv(posts_path, show_col_types = FALSE) %>%
    select(post_id, category, text, url)
  disagreements <- disagreements %>% left_join(posts, by = "post_id")
}

save_table(disagreements, "reliability_disagreements_for_adjudication.csv")

if (length(results) > 0) {
  reliability_summary <- bind_rows(results)
  save_table(reliability_summary, "reliability_summary.csv")
  print(reliability_summary)
} else {
  warning("No kappa values were computed from the provided data.")
}

message("Reliability outputs saved to outputs/tables and outputs/figures.")
```

::: {.callout-note}
## What is happening?
This imports coder ratings and computes:

- Cohen's kappa (two coders)
- Fleiss' kappa (more than two coders)
- confusion matrix
- disagreement rows for adjudication

Use disagreement output to resolve final coding decisions.
:::

# 7) Statistical Comparison of Stigma by Category

```{r section_07_stats_comparison}
#| eval: false
#| code-fold: true
#| code-summary: "Show statistical comparison code"
# 07 statistical comparison + final visuals

suppressPackageStartupMessages({
  library(tidyverse)
  library(effectsize)
  library(scales)
  library(here)
})

posts <- readr::read_csv(here::here("data_clean", "posts_clean.csv"), show_col_types = FALSE)

adjudicated_path <- here::here("docs", "codebook", "adjudicated_codes.csv")

if (!file.exists(adjudicated_path)) {
  stop(
    "Missing docs/codebook/adjudicated_codes.csv. Create an adjudicated file with at least post_id and stigma_binary.",
    call. = FALSE
  )
}

codes <- readr::read_csv(adjudicated_path, show_col_types = FALSE)

required_code_cols <- c("post_id", "stigma_binary")
missing_code_cols <- setdiff(required_code_cols, names(codes))
if (length(missing_code_cols) > 0) {
  stop(
    "Adjudicated file must include post_id and stigma_binary. Missing: ",
    paste(missing_code_cols, collapse = ", "),
    call. = FALSE
  )
}

analysis_df <- posts %>%
  select(post_id, category) %>%
  left_join(codes, by = "post_id") %>%
  mutate(
    category = normalise_category(category),
    stigma_binary = as.integer(stigma_binary)
  ) %>%
  filter(!is.na(category), !is.na(stigma_binary))

prevalence <- analysis_df %>%
  count(category, stigma_binary, name = "n") %>%
  group_by(category) %>%
  mutate(percent = 100 * n / sum(n)) %>%
  ungroup() %>%
  mutate(stigma_binary = factor(stigma_binary, levels = c(0, 1), labels = c("Absent", "Present")))

save_table(prevalence, "stigma_prevalence_by_category.csv")

contingency <- table(analysis_df$category, analysis_df$stigma_binary)
chi <- chisq.test(contingency, correct = FALSE)
effect <- effectsize::cramers_v(contingency)

chi_results <- tibble(
  test = "Chi-square test of stigma presence by category",
  statistic = unname(chi$statistic),
  df = unname(chi$parameter),
  p_value = chi$p.value,
  cramers_v = unname(effect$Cramers_v),
  interpretation = case_when(
    effect$Cramers_v < 0.10 ~ "Very small",
    effect$Cramers_v < 0.30 ~ "Small",
    effect$Cramers_v < 0.50 ~ "Medium",
    TRUE ~ "Large"
  )
)

save_table(chi_results, "stigma_chi_square_results.csv")

plot_prevalence <- prevalence %>%
  ggplot(aes(x = category, y = percent, fill = stigma_binary)) +
  geom_col(position = "stack") +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  scale_fill_manual(values = c("Absent" = "#6C757D", "Present" = "#B23A48")) +
  labs(
    title = "Weight Stigma Prevalence by Category",
    x = NULL,
    y = "Percent of posts",
    fill = "Stigma"
  ) +
  theme_minimal(base_size = 12)

save_plot(plot_prevalence, "stigma_prevalence_by_category.png")

multi_code_cols <- c(
  "explicit_blame",
  "moralising_food_body",
  "appearance_judgement",
  "stereotyping_larger_bodies",
  "healthism_personal_failure",
  "neutral_supportive"
)

available_multi_codes <- intersect(multi_code_cols, names(codes))

if (length(available_multi_codes) > 0) {
  multi_long <- analysis_df %>%
    pivot_longer(cols = all_of(available_multi_codes), names_to = "code", values_to = "present") %>%
    mutate(present = as.integer(present)) %>%
    filter(!is.na(present), present == 1) %>%
    count(category, code, name = "n")

  save_table(multi_long, "stigma_multicode_counts.csv")

  plot_multicode <- multi_long %>%
    ggplot(aes(x = n, y = reorder(code, n), fill = category)) +
    geom_col(position = "dodge") +
    labs(
      title = "Frequency of Stigma Subtypes by Category",
      x = "Count",
      y = NULL,
      fill = "Category"
    ) +
    theme_minimal(base_size = 12)

  save_plot(plot_multicode, "stigma_multicode_by_category.png")
}

message("Statistical outputs saved to outputs/tables and outputs/figures.")
```

::: {.callout-note}
## What is happening?
This joins final adjudicated codes to categories, calculates prevalence, runs chi-square tests, and reports effect size (Cramer's V).
:::

Required file before running section `7) Statistical Comparison of Stigma by Category`:

- `docs/codebook/adjudicated_codes.csv`

You can start from:

- `docs/codebook/adjudicated_codes_template.csv`

# Dissertation Write-up Templates

## Methods wording (example)

"Weight-stigmatising content was identified primarily through human coding using a predefined codebook. Posts were coded as stigma present versus absent, with additional subtype codes (e.g., explicit blame, moralising language, appearance judgement)."

"Lexicon-based sentiment analysis was conducted as a complementary exploratory method and was not used as a direct measure of weight stigma."

"Inter-rater reliability was evaluated using Cohen's kappa (two coders) and Fleiss' kappa when more than two coders were available."

## Results wording (placeholders)

"A total of **[N]** posts were analysed (**[n1] weight_loss**, **[n2] health_focused**)."

"Weight stigma was identified in **[x%]** of weight_loss posts and **[y%]** of health_focused posts."

"The association between post category and stigma presence was **[significant/not significant]** (chi-square(**[df]**) = **[value]**, p = **[value]**, Cramer's V = **[value]**)."

"Inter-rater agreement for binary stigma coding was **[kappa]**, indicating **[interpretation]** agreement."

# Caption Starters

- Figure: "Top terms by post category after stopword removal."
- Figure: "Most distinctive terms by category using TF-IDF."
- Figure: "Distribution of lexicon sentiment scores by post category."
- Figure: "Prevalence of weight stigma by post category."
- Table: "Inter-rater reliability statistics for stigma coding."

# Final Checklist

::: {.callout-tip}
## Before submission
- Confirm your final run used the real dataset in `data_raw/`.
- Keep all generated tables/figures in `outputs/`.
- Report stigma coding and sentiment as separate constructs.
- State limitations of lexicon methods clearly.
- Emphasise practical implications for dietetic communication and patient care.
:::
